Logistic Regression and SVM

### 2019-11-11 simple_ml/example/report2/paper.tex
start exp2.

% Write abstract here
\begin{abstract}
In this report, we solve the binary classification problem in a9a Dataset by using Logistic Regression (LR) and Support Vector Machine (SVM). \\
We perform experiments on four aspects: \\
1. Comparision between CFS optimized LR and CFS optimized RR. \\
2. Comparision between GD, SGD, MBGD in terms of convergence and time-cost. \\
3. Tuning learning rate in MBGD. \\
4. Comparision between CFS optimized and MBGD optimized LR. \\
\end{abstract}

>>>>

% Write abstract here
\begin{abstract}
In this report, we solve the binary classification problem in a9a dataset by Logistic Regression (LR) and Support Vector Machine (SVM). \\
We perform experiments on three aspects: \\
1. Loss function comparision in SVM. \\
2. Hyper-parameter tuning in SVM. \\
3. Initilizer comparision in both LR and SVM. \\
4. Optimizer comparision in both LR and SVM. \\
\end{abstract}
